### 2018-07-29 abstract.tex
Abstract added

\begin{abstract}
        % motivation
        % problem statement
        % approach
        % results
        % conclusions
\end{abstract}

>>>>

\begin{abstract}

Current interest in advanced nuclear energy and \gls{MSR} concepts has enhanced demand in building the tools to analyze these systems. This paper introduces a Python script, SaltProc, which simulates \gls{MSR} online reprocessing by modeling the changing isotopic composition of an irradiated fuel salt. SaltProc couples with the Monte Carlo code, SERPENT 2, for neutron transport and depletion calculations. SaltProc capabilities was illuminated for full-core depletion in the \gls{MSBR} which demonstrated that (1) equilibrium fuel composition could be achieved after 16 years and (2) the multiplication factor stabilizes after 6 years of operation. Fuel salt irradiation with online reprocessing causes considerable neutron energy spectrum hardening; this spectral shift has a problematic impact on safety parameters (e.g., temperature reactivity feedback, reactivity control system worth). Volatile gases and noble metals removal has positive effect on the core performance approximately 7500 pcm over 10-years timeframe; rare earth elements removal has slower rate and less impact on reactivity (5500 pcm). Finally, the average $^{232}$Th feed rate throughout 60 years of operation is 100 g/GWh$_e$ which is a good agreement with other recent research. Problematic effects of neutron energy spectrum hardening during \gls{MSBR} operation should be taken into account for neutronics, multi-physics, and fuel cycle performance analysis.

\end{abstract}

### 2018-07-29 introduction.tex
Abstract added

 In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{Transuranic elements}F$_3$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}. This innovation leads to immediate advantages over traditional, solid-fueled, reactors. These include near-atmospheric pressure in the primary loop, relatively high coolant temperature, outstanding neutron economy, a high level of inherent safety, reduced fuel preprocessing, and the ability to continuously remove fission products and add fissile and/or fertile elements \cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the early 1970s by \gls{ORNL} specifically to realize the promise of the thorium fuel cycle, which uses natural thorium instead of enriched uranium. With continuous fuel reprocessing, \gls{MSBR} is very attractive to effecively realize advantages of the thorium fuel cycle because the $^{233}$U bred from $^{232}$Th is almost instantly \footnote{$^{232}$Th transmutes into $^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U ($\tau_{1/2}$=26.967d).} being recycled back to the core \cite{betzler_modeling_2016}. The mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$ has a melting point of $499^\circ$C, a low vapor pressure at operating temperatures, and good flow and heat transfer properties \cite{robertson_conceptual_1971}. In the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. Finally, the \gls{MSR} also could be employed as a converter reactor for transmutation of spent fuel from current \glspl{LWR}.

>>>>

 In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic elements}F$_3$) are mixed with carrier salts to form a liquid fuel which is circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}. This innovation leads to immediate advantages over traditional, solid-fueled, reactors. These include near-atmospheric pressure in the primary loop, relatively high coolant temperature, outstanding neutron economy, a high level of inherent safety, reduced fuel preprocessing, and the ability to continuously remove fission products and add fissile and/or fertile elements \cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the early 1970s by \gls{ORNL} specifically to realize the promise of the thorium fuel cycle, which uses natural thorium instead of enriched uranium. With continuous fuel reprocessing, \gls{MSBR} is very attractive to effecively realize advantages of the thorium fuel cycle because the $^{233}$U bred from $^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into $^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U ($\tau_{1/2}$=26.967d).} being recycled back to the core \cite{betzler_modeling_2016}. The mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$ has a melting point of $499^\circ$C, a low vapor pressure at operating temperatures, and good flow and heat transfer properties \cite{robertson_conceptual_1971}. In the matter of nuclear fuel cycle, the thorium cycle produces a reduced quantity of plutonium and \glspl{MA} compared to the traditional uranium fuel cycle. Finally, the \gls{MSR} also could be employed as a converter reactor for transmutation of spent fuel from current \glspl{LWR}.

### 2018-07-29 results.tex
Abstract added

\subsection{Effective multiplication factor}
Figure~\ref{fig:keff} demonstrates the effective multiplication factors obtained using SaltProc and SERPENT 2. The effective multiplication factors are calculated after removing fission products listed in Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of ``cycle time"\footnote{The \gls{MSBR} program defined a ``cycle time" as the amount of time required to remove 100\% of a target nuclide from a fuel salt.} which was fixed at 3 days for this work. The effective multiplication factor fluctuates significantly as a result of the batch-wise nature of this online reprocessing strategy.

@@

The analysis of the fuel salt composition evolution provides more comprehensive information about the equilibrium state. Figure~\ref{fig:adens_eq} shows major nuclides which have a strong influence on the reactor core physics normalized separately for each isotope by average atomic density, at the beginning of each depletion time step. Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in fuel salt change insignificantly after approximately 2500 days of operation. Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time interval from 16 to 20 years of operation, hence,a quasi-equilibrium state was achieved after 16 years of reactor operation.
\begin{figure}[ht!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{major_isotopes_adens.png}
  \caption{Number density of major nuclides during 60 years of reactor operation.}
  \label{fig:adens_eq}
\end{figure}
In contrast, a wide variety of nuclides, including fissile isotopes (e.g. $^{235}$U) and non-fissile strong absorbers (e.g. $^{234}$U), keep accumulating in the core. Figure~\ref{fig:fissile_short} demonstrate production of fissile isotopes in the core. In the end of considered operational time the core contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu ($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ atom/b-cm). Meanwhile, the equilibrium number density of the target fissile isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Thus, production of new fissile materials in the core as well as $^{233}$U breeding make it possible to compensate for negative effects of strong absorber accumulation and keep the reactor critical.
\begin{figure}[htp!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{fissile_short.png}
  \caption{Number density of fissile in epithermal spectrum nuclides accumulation during the reactor operation.}
  \label{fig:fissile_short}
\end{figure}

@@

It is important to obtain the epithermal and thermal spectra to produce $^{233}$U from $^{232}$Th because the radiative capture cross section of thorium decreases monotonically from $10^{-10}$ MeV to $10^{-5}$ MeV. Hardening the spectrum tends to significantly increase resonance absorption in thorium and decrease the absorptions in fissile and construction materials. Thus, a significant amount fissile material will be needed to make the reactor critical.

@@

  \includegraphics[width=\textwidth]{spectrum_zones.png} 
  \caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
  \label{fig:spectrum_zones}
\begin{figure}[hb!] % replace 't' with 'b' to force it to 

@@

\begin{table}[hb!]

@@

\begin{figure}[hb!] % replace 't' with 'b' to force it to 

>>>>

\subsection{Effective multiplication factor}
Figure~\ref{fig:keff} demonstrates the effective multiplication factors obtained using SaltProc and SERPENT 2. The effective multiplication factors are calculated after removing fission products listed in Table~\ref{tab:reprocessing_list} and adding the fertile material at the end of ``cycle time"\footnote{ The \gls{MSBR} program defined a ``cycle time" as the amount of time required to remove 100\% of a target nuclide from a fuel salt.} which was fixed at 3 days for this work. The effective multiplication factor fluctuates significantly as a result of the batch-wise nature of this online reprocessing strategy.

@@

\subsection{Fuel salt composition dynamics}
The analysis of the fuel salt composition evolution provides more comprehensive information about the equilibrium state. Figure~\ref{fig:adens_eq} shows major nuclides which have a strong influence on the reactor core physics normalized separately for each isotope by average atomic density, at the beginning of each depletion time step. Concentration of $^{233}$U, $^{232}$Th, $^{233}$Pa, and $^{232}$Pa in fuel salt change insignificantly after approximately 2500 days of operation. Particularly, $^{233}$U number density fluctuates less than 0.8\% in the time interval from 16 to 20 years of operation, hence,a quasi-equilibrium state was achieved after 16 years of reactor operation.
\begin{figure}[ht!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{major_isotopes_adens.png}
  \caption{Number density of major nuclides during 60 years of reactor operation.}
  \label{fig:adens_eq}
\end{figure}
In contrast, a wide variety of nuclides, including fissile isotopes (e.g. $^{235}$U) and non-fissile strong absorbers (e.g. $^{234}$U), keep accumulating in the core. Figure~\ref{fig:fissile_short} demonstrate production of fissile isotopes in the core. In the end of considered operational time the core contains significant $^{235}$U ($\approx10^{-5}$ atom/b-cm), $^{239}$Pu ($\approx5\times10^{-7}$ atom/b-cm), and $^{241}$Pu ($\approx 5\times10^{-7}$ atom/b-cm). Meanwhile, the equilibrium number density of the target fissile isotope $^{233}$U was approximately 7.97$\times10^{-5}$ atom/b-cm. Thus, production of new fissile materials in the core as well as $^{233}$U breeding make it possible to compensate for negative effects of strong absorber accumulation and keep the reactor critical.
\begin{figure}[htp!] % replace 't' with 'b' to 
  \centering
  \includegraphics[width=\textwidth]{fissile_short.png}
  \caption{Number density of fissile in epithermal spectrum nuclides accumulation during the reactor operation.}
  \label{fig:fissile_short}
\end{figure}

@@

It is important to obtain the epithermal and thermal spectra to produce $^{233}$U from $^{232}$Th because the radiative capture cross section of thorium decreases monotonically from $10^{-10}$ MeV to $10^{-5}$ MeV. Hardening the spectrum tends to significantly increase resonance absorption in thorium and decrease the absorptions in fissile and construction materials. Thus, a significant amount fissile material will be needed to make the reactor critical. 
\begin{figure}[ht!] % replace 't' with 'b' to force it to 
  \centering
  \includegraphics[width=\textwidth]{spectrum_zones.png} 
  \caption{Neutron flux energy spectrum in different core regions normalized by unit lethargy for the initial and equilibrium fuel salt composition.}
  \label{fig:spectrum_zones}
\end{figure}

@@

@@

@@
